Towards a Machine Learning approach for Aggregate Computing

### 2021-11-28 paper-2021-woa-ac-ml.tex
Ref needed on slow-rising
Correct scafi citation + remove self-citations of little relevance here

AC is studied in various simulated scenarios ranging from smart cities to crowds, 
 thanks to Alchemist~\cite{DBLP:journals/jos/PianiniMV13} (a meta-simulator for pervasive systems) and to programming languages and toolchains that support 
 this paradigm, such as ScaFi~\cite{DBLP:conf/ecoop/CasadeiV16}, FCCP~\cite{DBLP:conf/acsos/Audrito20} and Protelis~\cite{PianiniSAC2015}.

@@

A naive implementation of this kind of problem can be described in AC as:
\begin{minted}[fontsize=\scriptsize]{scala}
def hopCount(): Int = {
  rep(Double.PositiveInfinity) { 
    hopCounts => mux(source) 
    { 0 } 
    { minHoodPlus(nbr{hopCounts}) + 1 }
  }
}
\end{minted}
However, this solution suffers from the slow-rising problem. 
 It consists of a slow convergence time when an equilibrium situation is broken.
So, our first intuition is to accelerate convergence through learning.
 In particular, the previous solution can be rewritten as:

>>>>

AC is studied in various simulated scenarios ranging from smart cities to crowds, 
 thanks to Alchemist~\cite{DBLP:journals/jos/PianiniMV13} (a meta-simulator for pervasive systems) and to programming languages and toolchains that support 
 this paradigm, such as ScaFi~\cite{DBLP:conf/isola/CasadeiVAD20}. %, FCCP~\cite{DBLP:conf/acsos/Audrito20} and Protelis~\cite{PianiniSAC2015}.

@@

A naive implementation of this kind of problem can be described in AC as:
\begin{minted}[fontsize=\scriptsize]{scala}
def hopCount(): Int = {
  rep(Double.PositiveInfinity) { 
    hopCounts => mux(source) 
    { 0 } 
    { minHoodPlus(nbr{hopCounts}) + 1 }
  }
}
\end{minted}
However, this solution suffers from the slow-rising problem~\cite{DBLP:conf/saso/AudritoCDV17}. 
 It consists of a slow convergence time when an equilibrium situation is broken.
So, our first intuition is to accelerate convergence through learning.
 In particular, the previous solution can be rewritten as:
